TUD Datasets: A collection of benchmark datasets for learning with graphs

### 2020-03-25 main.tex
MC.

\begin{abstract}
Recently, there has been an increasing interest in learning with graph data, especially in graph neural networks.  However, the development of meaningful benchmark datasets and standarized evaluation prodecures are lagging behind. That is, most paper papers evaluate their methods on small-scale datasets leading to high standard deviations and coseuqntly hindering advancements in this area. To adress this, we intodruce the \textsc{Tud benchmark dataset} for graph classification and regression. The dataset consists of over 150 datasets from a wide range of applications and variying size. We provide Python based data loaders, baseline implementations, and evaluation tools. Here, we give an overview of the datasets, the evalution tools, and provide baseline experiments. 
\end{abstract}

>>>>

\begin{abstract}
Recently, there has been an increasing interest in learning with graph data, especially using graph neural networks.  However, the development of meaningful benchmark datasets and standardized evaluation procedures is lagging behind. That is, most paper papers evaluate their methods on small-scale datasets leading to high standard deviations and hard to interpret results, consequently hindering advancements in this area. To address this, we introduce the \textsc{Tud benchmark dataset} for graph classification and regression. The dataset consists of over 150 datasets from a wide range of applications and varying sizes. We provide Python-based data loaders, baseline implementations, and evaluation tools. Here, we give an overview of the datasets, evaluation tools, and provide baseline experiments. 
\end{abstract}
